Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-04 paper/main.tex
in results, add references to tables/figures

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content. Some categories
were created in such a way to reflect the six stimulus categories used in the
visual localizer experiment. Some additional categories were created to
semantically cluster nouns into categories ``that were obvious to make
sense''.\todo{yeah, well, sounds shit but that's basically it}.
% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
More specifically, nouns were categorized by the clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table
A complete overview of all categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table. Minor corrections due to incorrectly applied rules were by the author (s.
Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and the
eight stimulus segments used during fMRI scanning).

@@

\section{Results}
% both stimuli
% group results for primary contrasts
% stability of contrasts
% individual PPAs

% AO stimulus
% Bland-Altman-Plots

@@

@@

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted location \citep{haeusler2016cutanno}.
% AO anno
For the analysis of the AO data, we extended another publicly available
annotation of speech \citep{haeusler2020speechanno}. We manually annotated words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns embedded in sentences spoken by
the narrator to describe the movie's missing visual content. Some categories
were created in such a way to reflect the six stimulus categories used in the
visual localizer experiment. Some additional categories were created to
semantically cluster nouns into categories ``that were obvious to make
sense''.\todo{yeah, well, sounds shit but that's basically it}.
% categories Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der
% Zeit.
More specifically, nouns were categorized by the clue they provide about the
cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old),
its inherent persons (female, female name; male, male name, person), a person's
appearance (face, head; body, bodypart), and a scene's inherent objects (object,
furniture).
% reference to table
A complete overview of all categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules (see
Table. Minor corrections due to incorrectly applied rules were by the author
(see Table \ref{tab:descr-nouns-counts} for the counts in the whole stimulus and
the eight stimulus segments used during fMRI scanning).

@@

\section{Results}

\subsection{stability contrasts}
See Figure \ref{fig:stability-slices}.
-> Tabelle machen

\subsection{primary contrasts}
See Figure \ref{fig:group-slices}.

AO stimulus; See Table \ref{tab:res-ao-group1}

AV stimulus; See Table \ref{tab:res-av-group1}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

\subsection{individual results}
See Figure \ref{fig:subs-thresh-ppa}; AO / AV to localizer ratios

@@

\subsection{Bland-Altman-Plots}
See Figure \ref{fig:bland-altman}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects}
    \label{fig:bland-altman}
\end{figure*}
